On the properties of projectile motion and quadratic air resistance

### 2016-02-22 Paper/main.tex
Align page 10
Align and d -> R

		y=v_0 \sin\theta\,t - \frac12gt^2 \implies y_{max} = v_0 \sin\theta\,t_{peak} - \frac12gt_{peak}^2\\\nonumber
		= v_0 \sin\theta\,\frac{v_0\sin\theta}{g} - \frac12g\Big({\frac{v_0\sin\theta}{g}}\Big)^2    = \frac{v_{0}^2\sin^2\theta}{2g}\nonumber

@@

	Let $d$ be the absolute length. It is then true that

@@

		d &= \sqrt{\Big(\frac{v_{0}^2\sin2\theta\sin\alpha}{g}\Big)^2 + \Big(\frac{v_{0}^2\sin2\theta\cos\alpha}{g}\Big)^2}\\\label{eq:distance}

@@

	In order to determine the maximum $d$ we will study the derivative of $d$ with respect to $\theta$.

@@

	Solving $\frac{\partial d}{\partial \theta} = 0$ gives the maxima of $d$

@@

	We only consider cases where $\theta \geq 0$. Plugging $\theta=\frac{\pi}{4}$ into our expression for $d$ yields the following result.

@@

		d = \frac{v_{0}^2\sin2\theta}{g} \implies d_{max} = \frac{v_{0}^2\sin\frac\pi2}{g} = \frac{v_{0}^2}{g}

@@

	We want to launch our projectile in a way so that it reaches a distance $d$. We can do this with either a predetermined angle of launch $\theta$ or a predetermined initial velocity $v_0$. From~\eqref{eq:distance} we know that the distance $d$ our object travels is specified by the following equation.

@@

		d = \frac{v_{0}^2\sin2\theta}{g}

@@

	From here we can define the functions $\theta(d, v_0)$ and $v_0(d, \theta)$.

@@

		\theta(d, v_0) &= \frac12\arcsin\Big(\frac{dg}{v_{0}^2}\Big)\\\nonumber
		v_0(d, \theta) &= \sqrt{\frac{dg}{\sin2\theta}}

@@

	Setting the second term as negative yields a negative time which is nonsense. We will therefore write it as positive from now on. We can now find the length of a parabola and see how it varies with a changing angle $\theta$. Let $R$ denote the range of the projectile and let it be given by $x(t_{max})$.

@@

		= -g\,\int \mu\,dt = w\,\mu+c_1 &= -g(\frac{at^2}{2}+t)+c_2\implies\\\nonumber
		w = \frac{-g(\frac{at^2}{2}+t)+C}{\mu} &= \frac{-gat^2}{2\mu}-\frac{gt}{\mu}+\frac{C}{\mu}

>>>>

		y&=v_0 \sin\theta\,t - \frac12gt^2 \implies y_{max} = v_0 \sin\theta\,t_{peak} - \frac12gt_{peak}^2\\\nonumber
		&= v_0 \sin\theta\,\frac{v_0\sin\theta}{g} - \frac12g\Big({\frac{v_0\sin\theta}{g}}\Big)^2    = \frac{v_{0}^2\sin^2\theta}{2g}\nonumber

@@

	Let $R$ be the range. It is then true that

@@

		R &= \sqrt{\Big(\frac{v_{0}^2\sin2\theta\sin\alpha}{g}\Big)^2 + \Big(\frac{v_{0}^2\sin2\theta\cos\alpha}{g}\Big)^2}\\\label{eq:distance}

@@

	In order to determine the maximum $R$ we will study the derivative of $R$ with respect to $\theta$.

@@

	Solving $\frac{\partial d}{\partial \theta} = 0$ gives the maxima of $R$

@@

	We only consider cases where $\theta \geq 0$. Plugging $\theta=\frac{\pi}{4}$ into our expression for $R$ yields the following result.

@@

		R = \frac{v_{0}^2\sin2\theta}{g} \implies R_{max} = \frac{v_{0}^2\sin\frac\pi2}{g} = \frac{v_{0}^2}{g}

@@

	We want to launch our projectile in a way so that it has the range $R$. We can do this with either a predetermined angle of launch $\theta$ or a predetermined initial velocity $v_0$. From~\eqref{eq:distance} we know that the range $R$ of our object is specified by the following equation.

@@

		R = \frac{v_{0}^2\sin2\theta}{g}

@@

	From here we can define the functions $\theta(R, v_0)$ and $v_0(R, \theta)$.

@@

		\theta(R, v_0) &= \frac12\arcsin\Big(\frac{Rg}{v_{0}^2}\Big)\\\nonumber
		v_0(R, \theta) &= \sqrt{\frac{Rg}{\sin2\theta}}

@@

	Setting the second term as negative yields a negative time when $y_0 > 0$ which is nonsense. We will therefore write it as positive from now on. We can now find the length of a parabola and see how it varies with a changing angle $\theta$. Let $R$ denote the range of the projectile and let it be given by $x(t_{max})$.

@@

		&= -g\,\int \mu\,dt = w\,\mu+c_1 = -g(\frac{at^2}{2}+t)+c_2\implies\\\nonumber
		w &= \frac{-g(\frac{at^2}{2}+t)+C}{\mu} = \frac{-gat^2}{2\mu}-\frac{gt}{\mu}+\frac{C}{\mu}
